Luminosity function and flux function\\ or\\ How far to the brightest beacon?

### 2015-12-15 luminosity.tex
Adjustment to n_r sentence; flowing -> following

The probability that the bright flux lies in the range between $F_{\rm bright}$ and $F_{\rm bright} + dF_{\rm bright}$, denoted $\mathcal{P} [F_{\rm bright}] dF_{\rm bright}$, is the joint probability that one of the targets has flux between $F_{\rm bright}$ and $F_{\rm bright} + dF_{\rm bright}$ and that all others have smaller flux.
The probability that one object has flux lower than $F'$ is
%%%
\begin{equation}
P [<F'] = \int _{-\infty} ^{F'}  P [F] \; dF 
\end{equation}
%%%
Noting that we have $n_r$ ways to select the target with the highest flux, this probability is:
%%%
\begin{equation}
\mathcal{P} [F_{\rm bright}] dF_{\rm bright} = n_r P [< F_{\rm bright}]^{n_r-1}  P[F_{\rm bright}] dF_{\rm bright} %\\
%&=& N_R P(F_{\rm max}) dF_{\rm max} \left[ 1 - P (> F_{\rm max}) \right]^{N_R-1} \\
%&\sim & N_R P(F_{\rm max}) dF_{\rm max} \left[ 1 - ( N_R -1 ) P (> F_{\rm max}) \right]
\end{equation}
%%%
Here, the right thing to do would be to take an infinite sum over integer values of $n_r$ with occurrence probability function, but for the sake of simplicity, here we simply assume $n_r$ computed by equation (\ref{eq:n_r}) is a good proxy.

The expected value of the maximum flux among the targets within a spherical shell at radius $r$ (with width $dr$), $\langle F_{\rm bright} \rangle$, is obtained by calculating the flowing integral. 
%%%
\begin{eqnarray}
\langle F_{\rm bright} \rangle &=& \int dF_{\rm bright} \, F_{\rm bright} \mathcal{P} [F_{\rm bright}] \\
&=& n_r \int dF_{\rm bright} F_{\rm bright} P [< F_{\rm bright}]^{n_r-1}  P[F_{\rm bright}]
\end{eqnarray}
%%%

>>>>

The probability that the bright flux lies in the range between $F_{\rm bright}$ and $F_{\rm bright} + dF_{\rm bright}$, denoted $\mathcal{P} [F_{\rm bright}] dF_{\rm bright}$, is the joint probability that one of the targets has flux between $F_{\rm bright}$ and $F_{\rm bright} + dF_{\rm bright}$ and that all others have smaller flux.
The probability that one object has flux lower than $F'$ is
%%%
\begin{equation}
P [<F'] = \int _{-\infty} ^{F'}  P [F] \; dF 
\end{equation}
%%%
Noting that we have $n_r$ ways to select the target with the highest flux, this probability is:
%%%
\begin{equation}
\mathcal{P} [F_{\rm bright}] dF_{\rm bright} = n_r P [< F_{\rm bright}]^{n_r-1}  P[F_{\rm bright}] dF_{\rm bright} %\\
%&=& N_R P(F_{\rm max}) dF_{\rm max} \left[ 1 - P (> F_{\rm max}) \right]^{N_R-1} \\
%&\sim & N_R P(F_{\rm max}) dF_{\rm max} \left[ 1 - ( N_R -1 ) P (> F_{\rm max}) \right]
\end{equation}
%%%
Strictly speaking, the mathematically correct thing to do here would be to take an infinite sum over integer values of $n_r$, weighted by the occurrence probability of that value of $n_r$.
However, it is a reasonable proxy (and considerably simpler) to simply use the expected value of $n_r$, as given by equation (\ref{eq:n_r}).

The expected value of the maximum flux among the targets within a spherical shell at radius $r$ (with width $dr$), $\langle F_{\rm bright} \rangle$, is obtained by calculating the following integral. 
%%%
\begin{eqnarray}
\langle F_{\rm bright} \rangle &=& \int dF_{\rm bright} \, F_{\rm bright} \mathcal{P} [F_{\rm bright}] \\
&=& n_r \int dF_{\rm bright} F_{\rm bright} P [< F_{\rm bright}]^{n_r-1}  P[F_{\rm bright}]
\end{eqnarray}
%%%
